ASHA 2023 Listening Effort Data Analysis

### 2023-10-27 ASHA 2023 Analysis/data_analysis.Rmd
troubleshooting pupil dilation visualization and analysis

@@

>>>>

data %>%
  # For this analysis, we are only looking at accurate repetition trials
  dplyr::filter(rep_acc == "accurate") %>%
  dplyr::group_by(timebins, speaker) %>%
  dplyr::summarize(pupil_dilation = mean(pupil.binned, na.rm = T),
                   pupil_se = sd(pupil.binned, na.rm = T)/sqrt(n())) %>%
  ggplot() +
  aes(x = timebins,
      y = pupil_dilation,
      color = speaker,
      fill = speaker) +
  geom_ribbon(aes(ymin = pupil_dilation - pupil_se, ymax = pupil_dilation + pupil_se), alpha = .3) +
  geom_line() +
  coord_cartesian(xlim = c(0,5000), ylim = c(-100, 200)) +
  labs(x = "Time (ms)", y = "Pupil Dilation (arbitrary units)", fill = "Speaker", color = "Speaker") +
  theme_bw() + 
  theme(legend.position = "bottom", aspect.ratio = 1)

@@

# Fully Unconditional Model

# Specifying the region of interest for analysis (500 ms to 1000 ms after relative offset of the trial)

pupil_roi <- data %>%
  # For this analysis, we are only analyzing pupil dilation for accurate responses
  dplyr::filter(rep_acc == "accurate") %>%
  # filtering out timebins below 500 (i.e., keeping timebins above 500 ms)
  dplyr::filter(timebins >= 500) %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::filter(timebins <= max(timebins) - 2000) %>%
  ungroup() %>%
  # For the purpose of modeling, we are centering time at 500 ms (i.e. the beginning ROI time)
  dplyr::mutate(time_c = timebins - 500)

# Creating polynomial variables for model

pupil_roi <- gazer::code_poly(pupil_roi, predictor = "time_c", 
                              poly.order = 3, orthogonal = T, draw.poly = F)

# specifying unconditional growth model for pupil data

m0 <- glmmTMB(pupil.binned ~ poly1 + poly2 + poly3 + 
                (poly1 + poly2 + poly3|subject) + 
                (poly1 + poly2 +poly3|code), 
              data = pupil_roi)
